Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Edit algorithm performance

On the exponential density scenario, the algorithm performs a single split independently
of the value of $b$, i.e.~the number of discretizations is independent of the
variability of the exponential function.
Therefore, the computation time would be increased in comparison to the homogeneous
density case due to this single split, but would be independent of the value of $b$.

@@

>>>>

On the exponential density scenario, the algorithm performs a single split independently
of the value of $b$.
Therefore, the computation time would be increased in comparison to the homogeneous
density case due to this single split, but would be independent of the variation of the
function.

@@

There are some elements related to the implementation of the algorithm and the
programming language used that may increase the computation time, e.g.~we found that
density function callbacks on a Python implementation plays an important role on the
computation time increase.
For simplicity, these elements were not taken into account, and because they are
dependent on the specific implementation of the algorithm, they cannot be generalized.
